---
title: "Example analysis note — {{PROJECT_NAME}}"
# Render defaults (format.html, knitr device) live in notes/_metadata.yml
# so every note inherits them. Override here only when this note needs to differ.
---

```{r setup}
#| include: false
targets::tar_load(example_summary)

n_species <- nrow(example_summary)
n_obs <- sum(example_summary$n_obs)
```

This note demonstrates the **Data Reference Policy**: every reported number is
pulled from the `targets` pipeline via `tar_load()` and interpolated inline —
never hard-coded in the prose.

We analyzed `r scales::comma(n_obs)` observations across `r n_species`
species.

::: {.callout-important}
## Never hard-code numbers in prose
Every reported value — counts, estimates, summary statistics — must come from the
`targets` pipeline via `tar_load()` and be interpolated inline, as above. A
hard-coded `3,847` silently goes stale the moment the data changes.
:::

```{r table}
#| echo: false
example_summary
```

Replace this note with your own analysis (see `SETUP.md`, step 8).

## Cross-note links

Link to sibling notes with their **`.qmd`** path — for example
[another analysis note](another-note.qmd), or a section anchor such as
[the model section](another-note.qmd#model). Keeping the `.qmd` extension in the
source is convenient for editing, GitHub browsing, and `tar_quarto()` dependency
resolution. The `notes/qmd-links-to-html.lua` filter (registered in
`notes/_metadata.yml`) rewrites these to `.html` at HTML render time, so the
rendered page points at the rendered note instead of its raw source. External
URLs (e.g. <https://quarto.org>) and non-`.qmd` links are left untouched.

::: {.callout-tip}
## Link against the source, not the render
Write cross-note links with the `.qmd` extension. The filter turns them into
`.html` only at render time, so editing, GitHub browsing, and `tar_quarto()`
dependency resolution all keep working.
:::

## Session information

Recording the environment in the rendered output makes the note
self-documenting: the R version, platform, and package versions that produced
these numbers travel with the artefact.

```{r session-info}
#| echo: false
sessioninfo::session_info()
```
